Generating Simulated Data

### 2021-04-09 docs/SimData.Rmd
almost a function

binwidths <- function(Lmin, Lmax, vonBk, Nsizebins){
  #optimal bin size is lower end
  binopt <- 0.23*Lmax^0.6

  #range gives initial default binwidth, all equal (range/Nbins)
  #or should it be max/nbins?
  #can use if no K estimated
  bindef <- (Lmax-Lmin)/Nsizebins

  #minmaxvonBK$BTS_fall_allbox_effic1 %>% group_by(species) %>% mutate(bindef = (maxlen)/5)

  #vonBk tells you how many fine bins for fast growth
  # threshold cumprod of 0.05 to define last bin? tiny growth increment
  # use binopt up to this threshold? 
  # plot(cumprod(rep(1, 160)*exp(-0.0386)), ylim=c(0,1), xlim=c(0,180)) #saithe
  # lines(cumprod(rep(1, 20)*exp(-1.4)), ylim=c(0,1), xlim=c(0,180)) #capelin
  # lines(cumprod(rep(1, 40)*exp(-0.163)), ylim=c(0,1), xlim=c(0,180)) #redfish
  # lines(cumprod(rep(1, 130)*exp(-0.344)), ylim=c(0,1), xlim=c(0,180)) #cod

  thresh <- 0.05
  which(cumprod(rep(1, Lmax)*exp(-vonBk)) > thresh) #gives 1 cm increments of fast growth?

  #

  #low vonBK is doesn't asympote, divide length range equally into nbins?

  #high vonBK asympotes quickly,

  #aggregate bins in multiples of optimal for bigger fish/slower growth to get Nsizebins

>>>>

estbinwidths <- function(Lmax, vonBk, Nsizebins, thresh = 0.05){
  #optimal bin size is lower end
  binopt <- 0.23*Lmax^0.6

  #range gives initial default binwidth, all equal (range/Nbins)
  #or should it be max/nbins?
  #can use if no K estimated
  bindef <- max(1,ceiling(Lmax/Nsizebins))

  #minmaxvonBK$BTS_fall_allbox_effic1 %>% group_by(species) %>% mutate(bindef = ceiling(maxlen/5))

  #vonBk tells you how many fine bins for fast growth
  #low vonBK is doesn't asympote, divide length range equally into nbins?
  #high vonBK asympotes quickly, 
  # threshold cumprod of 0.05 or 0.1 to define last bin? tiny growth increment
  # use binopt up to this threshold? 
  # plot(cumprod(rep(1, 160)*exp(-0.0386)), ylim=c(0,1), xlim=c(0,180)) #saithe
  # lines(cumprod(rep(1, 20)*exp(-1.4)), ylim=c(0,1), xlim=c(0,180)) #capelin
  # lines(cumprod(rep(1, 40)*exp(-0.163)), ylim=c(0,1), xlim=c(0,180)) #redfish
  # lines(cumprod(rep(1, 130)*exp(-0.344)), ylim=c(0,1), xlim=c(0,180)) #cod

  lenthresh <- max(which(cumprod(rep(1, Lmax)*exp(-vonBk)) > thresh)) #gives 1 cm increments of fast growth

  #put all lengths above this into one big bin, 
  binwidth.max <- Lmax-lenthresh

  #divide lengths below this by thresholds? for min 5 bins, use .5, .3, .2, .1, .05?
  # or divide equally into nbins-1 bins? equal may be best
  # hightest growth bin will be very small and we won't have fish in it
  # dont go smaller than binopt
  binwidth.gro <- max(ceiling(binopt), ceiling(lenthresh/(Nsizebins-1)))

  #aggregate bins in multiples of optimal for bigger fish/slower growth to get Nsizebins
  ifelse(binwidth.max > bindef, #& binwidth.max < 0.5*Lmax,
         binwidths <- c(rep(binwidth.gro, Nsizebins-1), binwidth.max),
         binwidths <- rep(bindef, Nsizebins))

  return(binwidths)
